Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2016-10-05 paper_aa.tex
AA format

\documentclass[preprint]{aastex}

@@

%\newcommand{\alephuv}{\textphnc{\ARaleph}$_{\mathrm{UV}}$}
%\newcommand{\alephha}{\textphnc{\ARaleph}$_{\mathrm{H}\alpha}$}
%\newcommand{\alephuvha}{\textphnc{\ARaleph}$_{0.66}$}
%\newcommand{\alephhb}{\textphnc{\ARaleph}$_{\mathrm{H}\beta}$}
\usepackage{lscape}
\usepackage{amsmath}
\newcommand{\alephuv}{f$_{\mathrm{esc}}$(0.16$\,\micron$)}
\newcommand{\alephha}{f$_{\mathrm{esc}}$(H$\alpha$)}
\newcommand{\alephuvha}{f$_{\mathrm{esc}}$(0.66$\,\micron$)}
\newcommand{\alephhb}{f$_{\mathrm{esc}}$(H$\beta$)}

@@

\author{Kyle Penner\altaffilmark{1}, Mark Dickinson\altaffilmark{2},
Benjamin Weiner\altaffilmark{3}, Hanae Inami\altaffilmark{2},
Jeyhan Kartaltepe\altaffilmark{2}, Janine Pforr\altaffilmark{4},
Hooshang Nayyeri\altaffilmark{5},
Susan Kassin\altaffilmark{6},
Casey Papovich\altaffilmark{7}, and
Alexandra Pope\altaffilmark{8}
}

\email{kdpenner@gmail.com}

\altaffiltext{1}{Laboratoire AIM, DSM/Irfu/SAp, CEA-Saclay,
91191 Gif-sur-Yvette, France}
\altaffiltext{2}{National Optical Astronomy Observatory,
Tucson, AZ 85719, USA}
\altaffiltext{3}{Department of Astronomy, University of Arizona,
Tucson, AZ 85721, USA}
\altaffiltext{4}{Laboratoire d'Astrophysique de Marseille, Aix
Marseille Universit\'e, 13388 Marseille cedex 13, France}
\altaffiltext{5}{Department of Physics \& Astronomy, University of California
Irvine, Irvine, CA 92697, USA}
\altaffiltext{6}{Space Telescope Science Institute, Baltimore, MD 21218, USA}
\altaffiltext{7}{Department of Physics \& Astronomy, Texas A\&M University,
College Station, TX 77843, USA}
\altaffiltext{8}{Department of Astronomy, University of Massachusetts Amherst,
Amherst, MA 01003, USA}

\begin{abstract}
Do spatial distributions of dust grains in galaxies have typical forms, as do
spatial distributions of stars?  We investigate whether or not the distributions
resemble
uniform foreground screens, as commonly assumed by the high-redshift galaxy
community.  We use rest-frame infrared,
ultraviolet, and H$\alpha$ line luminosities of dust-poor and dusty galaxies
at $z \sim 0$ and $z \sim 1$ to compare measured H$\alpha$ escape fractions
with those predicted by the Calzetti attenuation formula.  The predictions,
based on
UV escape fractions, overestimate the measured H$\alpha$ escape fractions for
all samples.  The
interpretation of this result for dust-poor $z \sim 0$ galaxies is that regions
with ionizing stars have more dust than regions with nonionizing UV-emitting
stars.  Dust distributions for these galaxies are nonuniform.  The
interpretation of the overestimates for dusty galaxies at both redshifts is
less clear.  If the Calzetti attenuation formula is inapplicable to these galaxies,
perhaps the disagreements are unphysical; perhaps dust distributions in
these galaxies are uniform.  If the attenuation formula does apply, then dusty
galaxies have nonuniform dust distributions; the distributions are more
uniform than they are in dust-poor galaxies.  A broad range of H$\alpha$ escape
fractions at a given UV escape fraction for $z \sim 1$ dusty galaxies, if real,
indicates diverse dust morphologies and the implausibility of the screen
assumption.
\end{abstract}

@@

Our study uses observations of the GOODS-S, COSMOS, and UDS regions.  A
catalog of \emph{Herschel}/PACS 100$\,\micron$ sources for GOODS-S comes from
\citet{magnelli13}; for COSMOS and UDS, we use catalogs produced for the
\emph{Herschel} survey of CANDELS regions (Inami et al., in prep).  A
100$\,\micron$ source is defined as a $\ge 3\sigma$ flux density measurement
from PSF fitting to a \emph{Spitzer}/MIPS 24$\,\micron$ source, which is based
on an IRAC 3.6$\,\micron$ source prior.  In GOODS-S, the catalog has
flux densities at 24, 70, 100, and 160$\,\micron$; in COSMOS and
UDS, the catalogs have flux densities at 24, 100, 160, 250, 350,
and 500$\,\micron$.  All flux densities are $\ge 3\sigma$.  We do not use the
250, 350, and 500$\,\micron$ flux
densities in the COSMOS and UDS catalogs, to avoid the effects of source
confusion on PSF fitting.  Including them changes our results negligibly.

We associate each 100$\,\micron$ source with a 1.6$\,\micron$ ($H$-band) source
in the
catalogs produced by CANDELS
\citep[Nayyeri et al., in prep;][]{galametz13,guo13}.  Each catalog has
broadband flux densities at many wavelengths, not all of which are common to the
other two.  We require the 1.6$\,\micron$ source to be a unique match
within 0.7$\arcsec$ of the position of the 100$\,\micron$ source's
3.6$\,\micron$ prior.  The match radius is an estimate for maximizing the
number of unique matches while minimizing the number of multiple matches.

The final quantity of interest for each matched source is an H$\alpha$ line
flux or flux limit.  These come from our reduction of observations from the
\emph{HST}/WFC3-IR grism survey 3D-\emph{HST} \citep{brammer12}.
We match each 100$\,\micron$ source to a counterpart in the direct image
accompanying the grism observations.  Two people in our group visually inspect
the counterpart's spectrum and then review and reconcile any discrepant redshift
assignments.  The
H$\alpha$ line falls in the grism's wavelength range for galaxies at
$0.7 < z < 1.5$.  The spectra have low enough wavelength resolution that the
H$\alpha$ and [N II] lines are blended; we assume that the line flux of [NII]
at $\lambda = 0.6583\,\micron$ is 0.3 times the H$\alpha$ line flux and that
the line flux of [N II] at $\lambda = 0.6548\,\micron$ is 0.1 times the
H$\alpha$ line flux.  The ratio of [N II] to H$\alpha$ line fluxes depends on
gas-phase metallicity so these values may be incorrect for some star-forming
galaxies.
The values will be correct for a significant fraction of galaxies in our
sample if the sample has a distribution of
gas-phase metallicity similar to that of low-redshift galaxies
\citep{kauffmann03}.  The values will be correct for a larger fraction of
galaxies in our sample if the sample has a distribution of gas-phase
metallicity similar to that of low-redshift galaxies which are luminous in
the near-IR \citep{weiner07}.  For each 1D spectrum with a visible and
uncontaminated
line complex, we fit a linear model to the continuum and Gaussian profiles to
the emission lines and extract the H$\alpha$ line flux.  The uncertainty on the
line flux comes from the covariance matrix times the fit's reduced $\chi^{2}$.
We replace $< 5\sigma$ H$\alpha$ line fluxes with limits.  We multiply the line
fluxes and limits by 1.1, the aperture correction.

Some sources will be at $0.7 < z < 1.5$ but will not have visible H$\alpha$
line flux.  To determine line flux upper limits for these sources, we match each
100$\,\micron$ source to a source with a spectroscopic redshift in
the catalogs of:
\citet{lefevre04,szokoly04,mignoli05,ravikumar07,vanzella08,
balestra10,fadda10,kurk13,santini14}; and M. Dickinson (private communication)
for GOODS-S;
\citet{yamada05,simpson12}; Simpson et al. (in prep.); and
Almaini et al. (in prep.) for UDS; and \citet{lilly09} for COSMOS.  Operationally both the
100$\,\micron$ and spectroscopic catalogs are matched to the CANDELS catalogs.
If the 100$\,\micron$ source has a spectroscopic redshift that is unconfirmed
by an uncontaminated grism spectrum, we estimate the widths of the invisible
Gaussian line profiles from the ratio of integrated flux density to peak
surface brightness for the region of the direct image surrounding the galaxy.
The direct
image is the image taken as part of the grism observations.  We then fit
the same model as above to the 1D spectrum and extract the H$\alpha$ line flux
uncertainty.  We use $5\sigma$ limits.  We are unable to determine limits for
galaxies observed by the grism that are undetected in the direct image.  Most
limits are in GOODS-S because the spectroscopic completeness is higher there
than it is in COSMOS or UDS.

To summarize, our high-redshift sample contains galaxies with: (1) detected
emission at 100$\,\micron$; (2) detected emission at 1.6$\,\micron$; and (3)
spectroscopically-determined redshifts at $0.7 < z < 1.5$.

@@

LBAs are a subset of galaxies from those in \citet{heckman05}.
\citet{heckman05} match galaxies detected in the \emph{GALEX} All-Sky Imaging
Survey to galaxies with spectra from SDSS observations.  The LBA sample contains
galaxies with: (1) luminosity at 0.153$\,\micron, 0.153 \times L_{0.153},
\ge 2 \times 10^{10} L_{\odot}$; (2) surface brightness $> 10^{9} L_{\odot}~
\mathrm{kpc}^{-2}$, for which the luminosity is measured at 0.153$\,\micron$
and the radius is the half-light radius at 0.35$\,\micron$ ($u$-band);
(3) $z < 0.3$; and (4) no evidence for emission from an AGN.

We use 24$\,\micron$ flux densities in the \emph{Spitzer} Heritage Archive.  Of
the 26 sources in \citet{overzier11}, 3 have unreliable 24$\,\micron$ flux
densities per the recommendations in the enhanced imaging products quick start
guide; these sources are excluded.  The remaining 23 galaxies have flux
densities at
0.15 and 0.23$\,\micron$ (NUV and FUV bands).
H$\alpha$ line
fluxes are from Overzier (private communication).  We
multiply the line fluxes by 1.67 as a fiber-aperture correction
\citep{overzier09}.

We also apply our method to a sample of low-redshift dusty galaxies, which have
relatively unknown dust properties.  \citet{hwang13} collate, for low-redshift
dust-obscured galaxies (DOGs) and a control sample: flux densities at
9, 12, 22, 25, 60, 100, and 140$\,\micron$, from \emph{IRAS}, \emph{AKARI}, and
\emph{WISE} observations; 0.15 and 0.23$\,\micron$ flux densities, from
\emph{GALEX} observations; and H$\alpha$ line fluxes, from SDSS observations.
A low-redshift DOG has either: (1) a flux density, $S_{\nu}$, at 9$\,\micron$ that is more
than 982 times its flux density at 0.22$\,\micron$; or (2) a flux density at
12$\,\micron$ that is more than 892 times its flux density at 0.22$\,\micron$.
A low-redshift control galaxy has a flux density at
12$\,\micron$ that is less than 892 times its flux density at 0.22$\,\micron$.
Among other criteria the sample of control galaxies is filled such that its
distributions of IR luminosities and stellar masses match those of the sample
of DOGs.
The fiber-aperture corrections for the H$\alpha$ line fluxes come from the
differences, in the accompanying 0.62$\,\micron$ ($r$-band) images, between
Petrosian flux
densities and flux densities in apertures with equal size to the fiber
apertures.

@@

We estimate a total IR luminosity (8--1000$\,\micron$; $L_{\mathrm{IR}}$) for
each galaxy.  We redshift the \citet{chary01} template spectral energy
distributions (SEDs) to the distance of each galaxy.  Each template SED has
an IR luminosity.  If the galaxy has one
measured flux density at a rest-frame wavelength between 8 and 1000$\,\micron$,
we find the redshifted SED that most closely matches that flux
density and multiply the IR luminosity of the SED by the ratio between actual
and predicted flux densities.  If the galaxy has two or more measured IR flux
densities, we introduce a multiplicative factor $f$ for each SED.  We find the
best-fit $f$ for each SED; the result is an $f$ and $\chi^{2}$ value.  We
choose the SED and its accompanying $f$ that results in the
minimum of all $\chi^{2}$ values.  The galaxy's $L_{\mathrm{IR}}$ is then $f$
times the IR luminosity of the SED.  In practice, all the high- and
low-redshift dusty galaxies have two or more measured IR flux densities, and
all the low-redshift dust-poor galaxies have one measured IR flux density.
%The uncertainty on $L_{\mathrm{IR}}$ comes from maintaining
%the signal-to-noise ratio of the flux density, in the single flux density
%case, or from $f$'s covariance matrix times its reduced $\chi^{2}$, in the
%$\chi^{2}$-fitting case.

\citet{overzier11}, in their footnote 14, find that the \citet{chary01} SEDs do
not fit low-redshift dust-poor galaxies as well as other SEDs.  They measured
IR flux density limits at 70 and 160$\,\micron$ as well as flux densities at
24$\,\micron$.  The footnote explains that the \citet{chary01} SEDs, when
fit to 24$\,\micron$ flux densities, predict flux densities at 70 and
160$\,\micron$ that fall above their upper limits.  Our IR luminosities are
high compared to theirs---on average, a factor of 1.4 times higher; at most, a
factor of 2.5 times higher.  We present results for both sets of IR
luminosities for the low-redshift dust-poor galaxies.

@@

For galaxies with UV emission from newly formed massive stars the continuum
between 0.125 and 0.263$\,\micron$ is approximately a power law with index
$\beta$:
\begin{equation}
S_{\lambda} = C\lambda^{\beta}
\end{equation}
where $S_{\lambda}$ is flux density and $\lambda$ is wavelength.
We use all measured flux densities and uncertainties in this rest-frame
wavelength range to fit for $\beta$ and the constant factor $C$ or
for their limits.  Measured flux densities may be negative---the sky aperture
may be brighter than the galaxy aperture---which
complicates our fitting procedure.  When a galaxy has only two measured flux
densities in the wavelength range, the solution for $\beta$ and $C$ is
analytic, so for a solution to exist the flux densities must be positive.  If
they both are, we make no cuts on their signal-to-noise ratio (S/N).
If the only positive flux density, among multiple measurements, is $> 3\sigma$,
we calculate a $\beta$ limit using that flux density and a $3\sigma$ limit for
another in the rest-frame wavelength range.  Whether the limit is an upper or
lower one depends on whether the detected flux density's wavelength is lower
or higher than the limit's wavelength.  We do not estimate a $\beta$ limit when
the only positive flux density, among multiple measurements, is $< 3\sigma$.
If more than two measured flux densities are positive, regardless of their S/N
and whether the surplus measurements are negative or positive, we minimize
$\chi^{2}$.
%The uncertainty on $\beta$ comes from the propagation of
%flux density uncertainties, in the analytic case, or from the covariance
%matrix times the reduced $\chi^{2}$, in the $\chi^{2}$-fitting case.

We estimate an emergent UV luminosity or a
limit at rest-frame 0.16$\,\micron$ for each galaxy using its redshift and
the power-law fit to the rest-frame UV flux densities.  We refer to the
luminosity as $0.16 \times L_{0.16}$.  Fig. \ref{lir_luv} shows the IR and UV
luminosities for all galaxies in our samples.  We emphasize that we use
the adjective ``dusty'' because the average galaxy in the sample has a lower
UV luminosity and a higher IR luminosity than does the average galaxy in the
``dust-poor'' sample.

@@

\begin{deluxetable}{llllllllllllll}
\tablecolumns{14}
\tablewidth{0pc}
\tablecaption{Measured and derived quantities for the sample at $z > 0.7$}
\tabletypesize{\tiny}
\tablehead{
\colhead{RA, IR} &
\colhead{Dec, IR} &
\colhead{RA, opt.} &
\colhead{Dec, opt.} &
\colhead{$z$} &
\colhead{$\beta$} &
\colhead{$\sigma_{\beta}$} &
\colhead{$0.16 \times L_{0.16}$} &
\colhead{$\sigma_{L_{0.16}}$} &
\colhead{$L_{\mathrm{H}\alpha}$} &
\colhead{$\sigma_{L_{\mathrm{H}\alpha}}$} &
\colhead{$L_{\mathrm{H}\alpha}$ lim.} &
\colhead{$L_{\mathrm{IR}}$} &
\colhead{$\sigma_{L_{\mathrm{IR}}}$} \\
%\colhead{UV SFR} &
%\colhead{H$\alpha$ SFR} &
%\colhead{H$\alpha$ SFR lim.} &
%\colhead{IR SFR} \\
\colhead{deg} &
\colhead{deg} &
\colhead{deg} &
\colhead{deg} &
\colhead{} &
\colhead{} &
\colhead{} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$} &
\colhead{$L_{\odot}$}
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$} &
%\colhead{M$_{\odot}$ yr$^{-1}$}
\startdata
\cutinhead{GOODS-S}
53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablenotemark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\

@@

53.163998 & -27.854301 & 53.164062 & -27.854292 & 1.299\tablenotemark{G} & -0.53 & 0.09 & 2.5e+09 & 2.1e+08 & 1.4e+08 & 2.2e+07 & \ldots & 1.9e+11 & 3.7e+10  \\

@@

53.022831 & -27.796343 & 53.022819 & -27.796360 & 0.898\tablenotemark{G} & -1.07 & 0.27 & 4.5e+09 & 2.9e+08 & 1.4e+08 & 9.2e+06 & \ldots & 1.1e+11 & 3.9e+09  \\

@@

53.143452 & -27.783209 & 53.143470 & -27.783213 & 1.429\tablenotemark{G} & 1.30 & 1.55 & 8.1e+08 & 8.5e+08 & \ldots & \ldots & 9.3e+07 & 8.0e+11 & 2.4e+10  \\

@@

\cutinhead{COSMOS}

>>>>

\documentclass[referee]{aa}

@@

%\newcommand{\alephuv}{\textphnc{\ARaleph}$_{\mathrm{UV}}$}
%\newcommand{\alephha}{\textphnc{\ARaleph}$_{\mathrm{H}\alpha}$}
%\newcommand{\alephuvha}{\textphnc{\ARaleph}$_{0.66}$}
%\newcommand{\alephhb}{\textphnc{\ARaleph}$_{\mathrm{H}\beta}$}
\usepackage{lscape}
\usepackage{amsmath}
\newcommand{\alephuv}{f$_{\mathrm{esc}}$(0.16$\,\mu$m)}
\newcommand{\alephha}{f$_{\mathrm{esc}}$(H$\alpha$)}
\newcommand{\alephuvha}{f$_{\mathrm{esc}}$(0.66$\,\mu$m)}
\newcommand{\alephhb}{f$_{\mathrm{esc}}$(H$\beta$)}

@@

\author{K. Penner\inst{\ref{inst1}}
\and M. Dickinson\inst{\ref{inst2}}
\and B. Weiner\inst{\ref{inst3}}
\and H. Inami\inst{\ref{inst2}}
\and J. Kartaltepe\inst{\ref{inst2}}
\and J. Pforr\inst{\ref{inst4}}
\and H. Nayyeri\inst{\ref{inst5}}
\and S. Kassin\inst{\ref{inst6}}
\and C. Papovich\inst{\ref{inst7}}
\and A. Pope\inst{\ref{inst8}}
}

\institute{Laboratoire AIM, DSM/Irfu/SAp, CEA-Saclay,
91191 Gif-sur-Yvette, France\email{kdpenner@gmail.com}\label{inst1}
\and National Optical Astronomy Observatory, Tucson, AZ 85719, USA\label{inst2}
\and Department of Astronomy, University of Arizona, Tucson, AZ 85721, USA\label{inst3}
\and Laboratoire d'Astrophysique de Marseille, Aix Marseille Universit\'e,
13388 Marseille cedex 13, France\label{inst4}
\and Department of Physics \& Astronomy, University of California
Irvine, Irvine, CA 92697, USA\label{inst5}
\and Space Telescope Science Institute, Baltimore, MD 21218, USA\label{inst6}
\and Department of Physics \& Astronomy, Texas A\&M University,
College Station, TX 77843, USA\label{inst7}
\and Department of Astronomy, University of Massachusetts Amherst,
Amherst, MA 01003, USA\label{inst8}}

\date{Received date / Accepted date}

\abstract{
Do spatial distributions of dust grains in galaxies have typical forms, as do
spatial distributions of stars?  We investigate whether or not the distributions
resemble
uniform foreground screens, as commonly assumed by the high-redshift galaxy
community.  We use rest-frame infrared,
ultraviolet, and H$\alpha$ line luminosities of dust-poor and dusty galaxies
at $z \sim 0$ and $z \sim 1$ to compare measured H$\alpha$ escape fractions
with those predicted by the Calzetti attenuation formula.  The predictions,
based on
UV escape fractions, overestimate the measured H$\alpha$ escape fractions for
all samples.  The
interpretation of this result for dust-poor $z \sim 0$ galaxies is that regions
with ionizing stars have more dust than regions with nonionizing UV-emitting
stars.  Dust distributions for these galaxies are nonuniform.  The
interpretation of the overestimates for dusty galaxies at both redshifts is
less clear.  If the Calzetti attenuation formula is inapplicable to these galaxies,
perhaps the disagreements are unphysical; perhaps dust distributions in
these galaxies are uniform.  If the attenuation formula does apply, then dusty
galaxies have nonuniform dust distributions; the distributions are more
uniform than they are in dust-poor galaxies.  A broad range of H$\alpha$ escape
fractions at a given UV escape fraction for $z \sim 1$ dusty galaxies, if real,
indicates diverse dust morphologies and the implausibility of the screen
assumption.}

\keywords{ISM: dust, extinction -- galaxies: ISM -- galaxies: high-redshift}

\titlerunning{The degeneracy between dust distributions and the attenuation formula}
\authorrunning{K. Penner et al.}

\maketitle

@@

Our study uses observations of the GOODS-S, COSMOS, and UDS regions.  A
catalog of \emph{Herschel}/PACS 100$\,\mu$m sources for GOODS-S comes from
\citet{magnelli13}; for COSMOS and UDS, we use catalogs produced for the
\emph{Herschel} survey of CANDELS regions (Inami et al., in prep).  A
100$\,\mu$m source is defined as a $\ge 3\sigma$ flux density measurement
from PSF fitting to a \emph{Spitzer}/MIPS 24$\,\mu$m source, which is based
on an IRAC 3.6$\,\mu$m source prior.  In GOODS-S, the catalog has
flux densities at 24, 70, 100, and 160$\,\mu$m; in COSMOS and
UDS, the catalogs have flux densities at 24, 100, 160, 250, 350,
and 500$\,\mu$m.  All flux densities are $\ge 3\sigma$.  We do not use the
250, 350, and 500$\,\mu$m flux
densities in the COSMOS and UDS catalogs, to avoid the effects of source
confusion on PSF fitting.  Including them changes our results negligibly.

We associate each 100$\,\mu$m source with a 1.6$\,\mu$m ($H$-band) source
in the
catalogs produced by CANDELS
\citep[Nayyeri et al., in prep;][]{galametz13,guo13}.  Each catalog has
broadband flux densities at many wavelengths, not all of which are common to the
other two.  We require the 1.6$\,\mu$m source to be a unique match
within 0.7$\arcsec$ of the position of the 100$\,\mu$m source's
3.6$\,\mu$m prior.  The match radius is an estimate for maximizing the
number of unique matches while minimizing the number of multiple matches.

The final quantity of interest for each matched source is an H$\alpha$ line
flux or flux limit.  These come from our reduction of observations from the
\emph{HST}/WFC3-IR grism survey 3D-\emph{HST} \citep{brammer12}.
We match each 100$\,\mu$m source to a counterpart in the direct image
accompanying the grism observations.  Two people in our group visually inspect
the counterpart's spectrum and then review and reconcile any discrepant redshift
assignments.  The
H$\alpha$ line falls in the grism's wavelength range for galaxies at
$0.7 < z < 1.5$.  The spectra have low enough wavelength resolution that the
H$\alpha$ and [N II] lines are blended; we assume that the line flux of [NII]
at $\lambda = 0.6583\,\mu$m is 0.3 times the H$\alpha$ line flux and that
the line flux of [N II] at $\lambda = 0.6548\,\mu$m is 0.1 times the
H$\alpha$ line flux.  The ratio of [N II] to H$\alpha$ line fluxes depends on
gas-phase metallicity so these values may be incorrect for some star-forming
galaxies.
The values will be correct for a significant fraction of galaxies in our
sample if the sample has a distribution of
gas-phase metallicity similar to that of low-redshift galaxies
\citep{kauffmann03}.  The values will be correct for a larger fraction of
galaxies in our sample if the sample has a distribution of gas-phase
metallicity similar to that of low-redshift galaxies which are luminous in
the near-IR \citep{weiner07}.  For each 1D spectrum with a visible and
uncontaminated
line complex, we fit a linear model to the continuum and Gaussian profiles to
the emission lines and extract the H$\alpha$ line flux.  The uncertainty on the
line flux comes from the covariance matrix times the fit's reduced $\chi^{2}$.
We replace $< 5\sigma$ H$\alpha$ line fluxes with limits.  We multiply the line
fluxes and limits by 1.1, the aperture correction.

Some sources will be at $0.7 < z < 1.5$ but will not have visible H$\alpha$
line flux.  To determine line flux upper limits for these sources, we match each
100$\,\mu$m source to a source with a spectroscopic redshift in
the catalogs of:
\citet{lefevre04,szokoly04,mignoli05,ravikumar07,vanzella08,
balestra10,fadda10,kurk13,santini14}; and M. Dickinson (private communication)
for GOODS-S;
\citet{yamada05,simpson12}; Simpson et al. (in prep.); and
Almaini et al. (in prep.) for UDS; and \citet{lilly09} for COSMOS.  Operationally both the
100$\,\mu$m and spectroscopic catalogs are matched to the CANDELS catalogs.
If the 100$\,\mu$m source has a spectroscopic redshift that is unconfirmed
by an uncontaminated grism spectrum, we estimate the widths of the invisible
Gaussian line profiles from the ratio of integrated flux density to peak
surface brightness for the region of the direct image surrounding the galaxy.
The direct
image is the image taken as part of the grism observations.  We then fit
the same model as above to the 1D spectrum and extract the H$\alpha$ line flux
uncertainty.  We use $5\sigma$ limits.  We are unable to determine limits for
galaxies observed by the grism that are undetected in the direct image.  Most
limits are in GOODS-S because the spectroscopic completeness is higher there
than it is in COSMOS or UDS.

To summarize, our high-redshift sample contains galaxies with: (1) detected
emission at 100$\,\mu$m; (2) detected emission at 1.6$\,\mu$m; and (3)
spectroscopically-determined redshifts at $0.7 < z < 1.5$.

@@

LBAs are a subset of galaxies from those in \citet{heckman05}.
\citet{heckman05} match galaxies detected in the \emph{GALEX} All-Sky Imaging
Survey to galaxies with spectra from SDSS observations.  The LBA sample contains
galaxies with: (1) luminosity at 0.153$\,\mu$m$, 0.153 \times L_{0.153},
\ge 2 \times 10^{10} L_{\odot}$; (2) surface brightness $> 10^{9} L_{\odot}~
\mathrm{kpc}^{-2}$, for which the luminosity is measured at 0.153$\,\mu$m
and the radius is the half-light radius at 0.35$\,\mu$m ($u$-band);
(3) $z < 0.3$; and (4) no evidence for emission from an AGN.

We use 24$\,\mu$m flux densities in the \emph{Spitzer} Heritage Archive.  Of
the 26 sources in \citet{overzier11}, 3 have unreliable 24$\,\mu$m flux
densities per the recommendations in the enhanced imaging products quick start
guide; these sources are excluded.  The remaining 23 galaxies have flux
densities at
0.15 and 0.23$\,\mu$m (NUV and FUV bands).
H$\alpha$ line
fluxes are from Overzier (private communication).  We
multiply the line fluxes by 1.67 as a fiber-aperture correction
\citep{overzier09}.

We also apply our method to a sample of low-redshift dusty galaxies, which have
relatively unknown dust properties.  \citet{hwang13} collate, for low-redshift
dust-obscured galaxies (DOGs) and a control sample: flux densities at
9, 12, 22, 25, 60, 100, and 140$\,\mu$m, from \emph{IRAS}, \emph{AKARI}, and
\emph{WISE} observations; 0.15 and 0.23$\,\mu$m flux densities, from
\emph{GALEX} observations; and H$\alpha$ line fluxes, from SDSS observations.
A low-redshift DOG has either: (1) a flux density, $S_{\nu}$, at 9$\,\mu$m that is more
than 982 times its flux density at 0.22$\,\mu$m; or (2) a flux density at
12$\,\mu$m that is more than 892 times its flux density at 0.22$\,\mu$m.
A low-redshift control galaxy has a flux density at
12$\,\mu$m that is less than 892 times its flux density at 0.22$\,\mu$m.
Among other criteria the sample of control galaxies is filled such that its
distributions of IR luminosities and stellar masses match those of the sample
of DOGs.
The fiber-aperture corrections for the H$\alpha$ line fluxes come from the
differences, in the accompanying 0.62$\,\mu$m ($r$-band) images, between
Petrosian flux
densities and flux densities in apertures with equal size to the fiber
apertures.

@@

We estimate a total IR luminosity (8--1000$\,\mu$m; $L_{\mathrm{IR}}$) for
each galaxy.  We redshift the \citet{chary01} template spectral energy
distributions (SEDs) to the distance of each galaxy.  Each template SED has
an IR luminosity.  If the galaxy has one
measured flux density at a rest-frame wavelength between 8 and 1000$\,\mu$m,
we find the redshifted SED that most closely matches that flux
density and multiply the IR luminosity of the SED by the ratio between actual
and predicted flux densities.  If the galaxy has two or more measured IR flux
densities, we introduce a multiplicative factor $f$ for each SED.  We find the
best-fit $f$ for each SED; the result is an $f$ and $\chi^{2}$ value.  We
choose the SED and its accompanying $f$ that results in the
minimum of all $\chi^{2}$ values.  The galaxy's $L_{\mathrm{IR}}$ is then $f$
times the IR luminosity of the SED.  In practice, all the high- and
low-redshift dusty galaxies have two or more measured IR flux densities, and
all the low-redshift dust-poor galaxies have one measured IR flux density.
%The uncertainty on $L_{\mathrm{IR}}$ comes from maintaining
%the signal-to-noise ratio of the flux density, in the single flux density
%case, or from $f$'s covariance matrix times its reduced $\chi^{2}$, in the
%$\chi^{2}$-fitting case.

\citet{overzier11}, in their footnote 14, find that the \citet{chary01} SEDs do
not fit low-redshift dust-poor galaxies as well as other SEDs.  They measured
IR flux density limits at 70 and 160$\,\mu$m as well as flux densities at
24$\,\mu$m.  The footnote explains that the \citet{chary01} SEDs, when
fit to 24$\,\mu$m flux densities, predict flux densities at 70 and
160$\,\mu$m that fall above their upper limits.  Our IR luminosities are
high compared to theirs---on average, a factor of 1.4 times higher; at most, a
factor of 2.5 times higher.  We present results for both sets of IR
luminosities for the low-redshift dust-poor galaxies.

@@

For galaxies with UV emission from newly formed massive stars the continuum
between 0.125 and 0.263$\,\mu$m is approximately a power law with index
$\beta$:
\begin{equation}
S_{\lambda} = C\lambda^{\beta}
\end{equation}
where $S_{\lambda}$ is flux density and $\lambda$ is wavelength.
We use all measured flux densities and uncertainties in this rest-frame
wavelength range to fit for $\beta$ and the constant factor $C$ or
for their limits.  Measured flux densities may be negative---the sky aperture
may be brighter than the galaxy aperture---which
complicates our fitting procedure.  When a galaxy has only two measured flux
densities in the wavelength range, the solution for $\beta$ and $C$ is
analytic, so for a solution to exist the flux densities must be positive.  If
they both are, we make no cuts on their signal-to-noise ratio (S/N).
If the only positive flux density, among multiple measurements, is $> 3\sigma$,
we calculate a $\beta$ limit using that flux density and a $3\sigma$ limit for
another in the rest-frame wavelength range.  Whether the limit is an upper or
lower one depends on whether the detected flux density's wavelength is lower
or higher than the limit's wavelength.  We do not estimate a $\beta$ limit when
the only positive flux density, among multiple measurements, is $< 3\sigma$.
If more than two measured flux densities are positive, regardless of their S/N
and whether the surplus measurements are negative or positive, we minimize
$\chi^{2}$.
%The uncertainty on $\beta$ comes from the propagation of
%flux density uncertainties, in the analytic case, or from the covariance
%matrix times the reduced $\chi^{2}$, in the $\chi^{2}$-fitting case.

We estimate an emergent UV luminosity or a
limit at rest-frame 0.16$\,\mu$m for each galaxy using its redshift and
the power-law fit to the rest-frame UV flux densities.  We refer to the
luminosity as $0.16 \times L_{0.16}$.  Fig. \ref{lir_luv} shows the IR and UV
luminosities for all galaxies in our samples.  We emphasize that we use
the adjective ``dusty'' because the average galaxy in the sample has a lower
UV luminosity and a higher IR luminosity than does the average galaxy in the
``dust-poor'' sample.

@@

%\tablecolumns{14}
%\tablewidth{0pc}
\tiny
\begin{longtable}{llllllllllllll}
\caption{Measured and derived quantities for the sample at $z > 0.7$} \\
\hline \hline
RA, IR &
Dec, IR &
RA, opt. &
Dec, opt. &
$z$ &
$\beta$ &
$\sigma_{\beta}$ &
$0.16 \times L_{0.16}$ &
$\sigma_{L_{0.16}}$ &
$L_{\mathrm{H}\alpha}$ &
$\sigma_{L_{\mathrm{H}\alpha}}$ &
$L_{\mathrm{H}\alpha}$ lim. &
$L_{\mathrm{IR}}$ &
$\sigma_{L_{\mathrm{IR}}}$ \\
%{UV SFR} &
%{H$\alpha$ SFR} &
%{H$\alpha$ SFR lim.} &
%{IR SFR} \\
deg &
deg &
deg &
deg &
 &
 &
 &
$L_{\odot}$ &
$L_{\odot}$ &
$L_{\odot}$ &
$L_{\odot}$ &
$L_{\odot}$ &
$L_{\odot}$ &
$L_{\odot}$ \\
%{M$_{\odot}$ yr$^{-1}$} &
%{M$_{\odot}$ yr$^{-1}$} &
%{M$_{\odot}$ yr$^{-1}$} &
%{M$_{\odot}$ yr$^{-1}$}
\hline
\multicolumn{14}{c}{GOODS-S} \\
\hline
53.113487 & -27.933195 & 53.113470 & -27.933294 & 1.098\tablefootmark{G} & 0.53 & 0.34 & 1.1e+10 & 4.9e+08 & 5.6e+08 & 2.1e+07 & \ldots & 6.2e+11 & 1.9e+10  \\

@@

53.163998 & -27.854301 & 53.164062 & -27.854292 & 1.299\tablefootmark{G} & -0.53 & 0.09 & 2.5e+09 & 2.1e+08 & 1.4e+08 & 2.2e+07 & \ldots & 1.9e+11 & 3.7e+10  \\

@@

53.022831 & -27.796343 & 53.022819 & -27.796360 & 0.898\tablefootmark{G} & -1.07 & 0.27 & 4.5e+09 & 2.9e+08 & 1.4e+08 & 9.2e+06 & \ldots & 1.1e+11 & 3.9e+09  \\

@@

53.143452 & -27.783209 & 53.143470 & -27.783213 & 1.429\tablefootmark{G} & 1.30 & 1.55 & 8.1e+08 & 8.5e+08 & \ldots & \ldots & 9.3e+07 & 8.0e+11 & 2.4e+10  \\

@@

\hline
\multicolumn{14}{c}{COSMOS} \\
\hline
